%%%%%%%%%%%%%%%%%%%%% chapter.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample chapter
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%
%\motto{Use the template \emph{chapter.tex} to style the various elements of your chapter content.}

\chapter{I am a little little bird of IT}
\label{intro} % Always give a unique label
% use \chaptermark{}
% to alter or adjust the chapter heading in the running head

\abstract{An interesting book of IT carrer.}

\section{Yudong Jiang: Heart Breakup in CS Dep.}
\label{sec:1}

Yudong may be a smart and hard-working student, but he lives in a bad environment, I think. He knows what is bad, but he doesn't avoid it.

He has something common with me. We both complain about our surroundings, and we do something, but we don't do much.

Things are bad, yet, but not very bad. We still can do our best to gain much.

We are all the same in time, but we just do different things in the same time.

What we have done, is just what we should do. And we should do better, of course, our best.

\textcolor{red}{Doing better than others around you, may be doing bad than others far away from you.}

I am stupid yet, and this is true. And in future, I will find out this. Don't be embarrassed.

This is just what I should do.

\section{Shuai Liu: Seek for Hope in Despondence}
\label{sec:2}

Think much, in details. Ask why as often as you can.

\section{Xinxing Gu: Seek for the blue sea for yourself}

\label{sec:3}

Read website \emph{TechCrunch}, \emph{Wired} for new products and services of IT:

\textit{What problems does the product solve?\\
\indent
Does the problems exist before?\\
\indent
How to find the problems?\\
\indent
Which part of the problems remains unsolved?}

Management of your position, yourself. Structure mind. 4C, 4P or MECE.

English is important.

Technical interview:

Understanding the problems, trivial algorithms, optimized algorithms, the complexities.

Microsoft: Stability is everything.

\section{Yawei Tang: keep climbing though it is difficult}
\label{sec:4}

Intern time: 4,5,6

Confident though the interviewers list many conditions for the positions.

Prepare for the positions specially.

\section{You Xu: deep in the books hole}
\label{sec:5}

Learning programming language:

Type every char in the book, solve every problem.

My base knowledge is too weak, though I know something, I don't know the details.


